Development of Performance Regression Analysis Tool using Distributed Tracing on microservice-based Application\\

### 2022-09-13 paper.tex
txs auto checkin

\subsection{A Real-time Trace-level Root-cause Diagnosis System in Alibaba Datacenters}
This study \cite{rca-alibaba} uses distributed tracing to perform
Diagnostics of performance degradation on a system by performing graph analysis on
trace level in real-time to determine the root cause of performance degradation or
root cause. This approach was developed based on performance profiling, tracking, and logging system in Alibaba datacenter to speed up root cause diagnosis in real-time. The developed system allows the discovery of normative patterns and corresponding key graph properties, which are saved and updated offline as a knowledge base for further use in risk estimation at the trace level and identify transitions that are unexpected deviations from the normal
normal as shown in Fig. \ref{rca-framwork}.
\begin{figure}[htb]
	\centering
	\includegraphics[width=0.5\textwidth]{resources/ch2/rca-framework.png}
	\caption{Workflow of Root-cause Analysis on \cite{rca-alibaba}}
	\label{rca-framwork}
\end{figure}

@@

\subsection{Overhead Testing}
Of the 11 test cases, the average PRA Engine tool uses 0.046
vCPU with standard deviation of 0.0038 and 154.41 MiB Memory with standard
deviation of 17.91 in one analysis. The entire cluster has resources
as much as 6 vCPUs and 22.5 GiB, so that in one time doing PRA Engine analysis
resulting in CPU overhead as much as 0.78\% and Memory as much as 0.67\% to the Kubernetes cluster. Overhead caused by the tool is low so that the use of PRA Engine tools will have no impact on the overall performance of the Kubernetes cluster. Tab. \ref{overhead-tbl} shows the result of the overhead testing.
\begin{table}[!htb]
	\caption{Overhead testing result}
	\label{overhead-tbl}
	\centering
	\begin{tabular}{|l|c|c|}
		\hline
		\multicolumn{1}{|l|}{ID} & \multicolumn{1}{l|}{CPU (vCPU)} & \multicolumn{1}{l|}{Memory (MiB)} \\ \hline
		\textbf{IS1}     & 0,042 & 137,82  \\ \hline
		\textbf{IS2}     & 0,043 & 128,71  \\ \hline
		\textbf{IS3}     & 0,04  & 131,55  \\ \hline
		\textbf{IS4}     & 0,045 & 146,6   \\ \hline
		\textbf{IS5}     & 0,046 & 153,61  \\ \hline
		\textbf{IS6}     & 0,047 & 152,71  \\ \hline
		\textbf{IS7}     & 0,048 & 152,71  \\ \hline
		\textbf{ES1}     & 0,049 & 168,8   \\ \hline
		\textbf{ES2}     & 0,05  & 183,68  \\ \hline
		\textbf{ES3}     & 0,051 & 176,59  \\ \hline
		\textbf{ES4}     & 0,052 & 165,75  \\ \hline
		\textbf{Average} & 0,046 & 154,411 \\ \hline
		\textbf{STD}     & 0,038 & 17,916  \\ \hline
	\end{tabular}
\end{table}
\pagebreak
%
\section{Analysis}
Of all the test cases, the results obtained from the test will be
depending on the significant value used to test each case.
There are 3 significant values that the author uses to perform the test, namely 0.1, 0.005, and 0.001 with the aim of testing the sensitivity of the detection algorithm regressions are given different significant values. The result is a test with
a significant value of 0.1 successfully detects and analyzes the cause of the regression with true in all test cases, but in tests with a significant value of 0.05 and 0.001 SI1 cases were not detected as regression.

>>>>

\subsection{A Real-time Trace-level Root-cause Diagnosis System in Alibaba Datacenters}
This study \cite{rca-alibaba} uses distributed tracing to perform
Diagnostics of performance degradation on a system by performing graph analysis on
trace level in real-time to determine the root cause of performance degradation or
root cause. This approach was developed based on performance profiling, tracking, and logging system in Alibaba datacenter to speed up root cause diagnosis in real-time. The developed system allows the discovery of normative patterns and corresponding key graph properties, which are saved and updated offline as a knowledge base for further use in risk estimation at the trace level and identify transitions that are unexpected deviations from the normal.
%normal as shown in Fig. \ref{rca-framwork}.
%\begin{figure}[htb]
%	\centering
%	\includegraphics[width=0.5\textwidth]{resources/ch2/rca-framework.png}
%	\caption{Workflow of Root-cause Analysis on \cite{rca-alibaba}}
%	\label{rca-framwork}
%\end{figure}

@@

\subsection{Overhead Testing}
Of the 11 test cases, the average PRA Engine tool uses 0.046
vCPU with standard deviation of 0.0038 and 154.41 MiB Memory with standard
deviation of 17.91 in one analysis. The entire cluster has resources
as much as 6 vCPUs and 22.5 GiB, so that in one time doing PRA Engine analysis
resulting in CPU overhead as much as 0.78\% and Memory as much as 0.67\% to the Kubernetes cluster. Overhead caused by the tool is low so that the use of PRA Engine tools will have no impact on the overall performance of the Kubernetes cluster. Tab. \ref{overhead-tbl} shows the result of the overhead testing.

\begin{table}[!htb]
	\caption{Overhead testing result}
	\label{overhead-tbl}
	\centering
	\begin{tabular}{|l|c|c|}
		\hline
		\multicolumn{1}{|l|}{ID} & \multicolumn{1}{l|}{CPU (vCPU)} & \multicolumn{1}{l|}{Memory (MiB)} \\ \hline
		\textbf{IS1}     & 0,042 & 137,82  \\ \hline
		\textbf{IS2}     & 0,043 & 128,71  \\ \hline
		\textbf{IS3}     & 0,04  & 131,55  \\ \hline
		\textbf{IS4}     & 0,045 & 146,6   \\ \hline
		\textbf{IS5}     & 0,046 & 153,61  \\ \hline
		\textbf{IS6}     & 0,047 & 152,71  \\ \hline
		\textbf{IS7}     & 0,048 & 152,71  \\ \hline
		\textbf{ES1}     & 0,049 & 168,8   \\ \hline
		\textbf{ES2}     & 0,05  & 183,68  \\ \hline
		\textbf{ES3}     & 0,051 & 176,59  \\ \hline
		\textbf{ES4}     & 0,052 & 165,75  \\ \hline
		\textbf{Average} & 0,046 & 154,411 \\ \hline
		\textbf{STD}     & 0,038 & 17,916  \\ \hline
	\end{tabular}
\end{table}

%
\section{Analysis}
Of all the test cases, the results obtained from the test will be
depending on the significant value used to test each case.
There are 3 significant values that the author uses to perform the test, namely 0.1, 0.005, and 0.001 with the aim of testing the sensitivity of the detection algorithm regressions are given different significant values. The result is a test with
a significant value of 0.1 successfully detects and analyzes the cause of the regression with true in all test cases, but in tests with a significant value of 0.05 and 0.001 SI1 cases were not detected as regression.
